A Physically Motivated Framework to Compare Merger Timescales\\ of Isolated Low- and High-Mass Galaxy Pairs Across Cosmic Time

### 2024-03-31 paper/main.tex
Updates from Overleaf

        \begin{figure}[tb]
            \centering
            \includegraphics[width=\columnwidth]{plots/bet-on-it/8_timescale_mod.png}
            \caption{The median merger timescale as a function of redshift for low-mass (green) and high-mass (pink) pairs in our merger sample. 
            Shaded regions represent the 1st and 3rd quartile spread on the median. 
            % 
            The thick dotted black line at low redshifts shows the time to $z=0$ (the lookback time) as a function of redshift, which sets the upper bound for the merger timescale that a merging pair can have. 
            The thin black line shows the Hubble time as a function of redshift multiplied by a constant $XX$, which approximates the median time until merger from $z=6$ to $z\sim1$.
            %
            The median time until merger is similar for low-mass and high-mass pairs, and rises from $z=6$ to a peak at $z\sim0.75$, then decreases to $z=0$.\kc{update}}
            \label{fig:timescales}
        \end{figure}

@@

        In Fig.~\ref{fig:timescales}, the black dashed line shows the Hubble time $1/H(z)$ multiplied by XXX. 
        We did not perform a fit for this multiplicative constant, since we are interested in investigating the behavior of the merger timescale as a function of redshift rather than the specific values of the merger timescale. 
        The redshift evolution of our median merger timescales is consistent with the scaling with $1/H(z)$ between $z=\sim1-6$.\footnote{$H(z)$ is calculated using the same cosmology as the TNG100 simulation, from~\citet{Planck2018}. Specifically, $\Omega_M=0.31$ and $\Omega_{\Lambda}=0.69$.}

@@

        The median merger timescale for low-mass pairs does not change significantly for any separation cuts above $150\,\kpc$, which is larger than the average virial radius of low-mass systems at all redshifts. 
        On the other hand, high-mass merger timescales tend to increase as separation increases.
        % This is because selecting all pairs with $\rsep<200\,\kpc$ in a low-mass system is including a larger volume of the FoF halo, and thus a more complete selection of the full sample.
        High-mass pairs tend to have higher separations than low-mass pairs, as shown in Sec.~\ref{sec:results-timevsep}, due to the larger size of the high-mass subhalos. 
    \begin{figure*}[htb]
        \centering
        \includegraphics[width=\textwidth]{plots/bet-on-it/3_time_til_merger.png}
        \caption{(Top) The median merger timescale as a function of redshift for low-mass (green) and high-mass (pink) pairs with 3D physical separations greater than $10\,\kpc$ and less than $50,70,100,150,200,\mbox{and }300\,\kpc$ from left to right. 
        (Bottom) The median time until merger as a function of redshift for pairs with physical separations greater than $10\,\kpc$ and less than $0.25, 0.5, 1, 1.5, 2,\mbox{and }2.5\,\Rvir$ from left to right. 
        % 
        The thin black line is the same as shown in Fig.~\ref{fig:timescales}, and goes as the Hubble time $1/H(z)$.
        The time until merger increases from $z=4$ to $z\sim0.5-0.75$, at which point the time until merger decreases to zero since all low redshift mergers must have short merger timescales to merge before the end of the simulation at $z=0$. 
        \kc{H(z), "merger timescale"}
        }
        \label{fig:timescales-sep}
    \end{figure*}  
    \subsubsection{Scaled Separation Selected Pairs}
    \label{sec:results-scal}
        We calculate the merger timescales for six additional subsamples of pairs, applying separation criteria that scale with both redshift and mass.
        The scaled separation, which we define in Section~\ref{sec:methods}, is the separation of a pair divided by the virial radius of the pair's FoF group, $\Rvir$. 
        Scaled separation criteria select the equivalent \textit{fraction} of the full volume of each FoF group, regardless of mass or redshift, whereas physical separation criteria will select the same volume around each primary, with no account for the growth of dark matter halos or spatial distributions of satellites. 
        The scaled separation selected pairs have separations greater than $10\,\kpc$ and less than $[0.25, 0.5, 1, 1.5, 2, 2.5]\,\Rvir$. 
        As in the previous section, the selection criteria are applied at each redshift independently.

>>>>

        \begin{figure}[tb]
            \centering
            \includegraphics[width=\columnwidth]{plots/bet-on-it/8_timescale.png}
            \caption{The median merger timescale as a function of redshift for low-mass (green) and high-mass (pink) pairs in our merger sample. 
            Shaded regions represent the 1st and 3rd quartile spread on the median. 
            % 
            The thick dotted black line at low redshifts shows the time to $z=0$ (the lookback time) as a function of redshift, which sets the upper bound for the merger timescale that a merging pair can have. 
            The thin black line shows the Hubble time as a function of redshift multiplied by a constant $\beta=0.35$, which approximates the median time until merger from $z=6$ to $z\sim1$.
            %
            The median time until merger is similar for low-mass and high-mass pairs, and rises from $z=6$ to a peak at $z\sim0.75$, then decreases to $z=0$.}
            \label{fig:timescales}
        \end{figure}

@@

        In Fig.~\ref{fig:timescales}, the black dashed line shows the Hubble time $1/H(z)$ multiplied by $\beta=0.35$. 
        We did not perform a fit for this multiplicative constant, since we are interested in investigating the behavior of the merger timescale as a function of redshift rather than the specific values of the merger timescale. 
        The redshift evolution of our median merger timescales is consistent with the scaling with $1/H(z)$ between $z=\sim1-6$.\footnote{$H(z)$ is calculated using the same cosmology as the TNG100 simulation, from~\citet{Planck2018}. Specifically, $\Omega_M=0.31$ and $\Omega_{\Lambda}=0.69$.}

@@

        The median merger timescale for low-mass pairs does not change significantly for any separation cuts above $150\,\kpc$, which is larger than the average virial radius of low-mass systems at all redshifts. 
        On the other hand, high-mass merger timescales tend to increase as separation increases.
        % This is because selecting all pairs with $\rsep<200\,\kpc$ in a low-mass system is including a larger volume of the FoF halo, and thus a more complete selection of the full sample.
        High-mass pairs tend to have higher separations than low-mass pairs, as shown in Sec.~\ref{sec:results-timevsep}, due to the larger size of the high-mass subhalos. 
    \begin{figure*}[htb]
        \centering
        \includegraphics[width=\textwidth]{plots/bet-on-it/8_timescale_sepcut.png}
        \caption{(Top) The median merger timescale as a function of redshift for low-mass (green) and high-mass (pink) pairs with 3D physical separations greater than $10\,\kpc$ and less than $50,70,100,150,200,\mbox{and }300\,\kpc$ from left to right. 
        (Bottom) The median time until merger as a function of redshift for pairs with physical separations greater than $10\,\kpc$ and less than $0.25, 0.5, 1, 1.5, 2,\mbox{and }2.5\,\Rvir$ from left to right. 
        % 
        The thin black line is the same as shown in Fig.~\ref{fig:timescales}, and goes as the Hubble time $1/H(z)$ multiplied by 0.35 (see Sec.~\ref{sec:results-timevredshift} for additional details).
        The time until merger increases from $z=4$ to $z\sim0.5-0.75$, at which point the time until merger decreases to zero since all low redshift mergers must have short merger timescales to merge before the end of the simulation at $z=0$. 
        }
        \label{fig:timescales-sep}
    \end{figure*}  
    \subsubsection{Scaled Separation Selected Pairs}
    \label{sec:results-scal}
        We calculate the merger timescales for six additional subsamples of pairs, applying separation criteria that scale with both redshift and mass.
        The scaled separation, which we define in Section~\ref{sec:methods}, is the separation of a pair divided by the virial radius of the pair's FoF group, $\Rvir$. 
        Scaled separation criteria select the equivalent \textit{fraction} of the full volume of each FoF group, regardless of mass or redshift, whereas physical separation criteria will select the same volume around each primary, with no account for the growth of dark matter halos or spatial distributions of satellites. 
        The scaled separation selected pairs have separations greater than $10\,\kpc$ and less than $[0.25, 0.5, 1, 1.5, 2, 2.5]\,\Rvir$. 
        As in the previous section, the selection criteria are applied at each redshift independently.
